Hydras and Cie \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-23 doc/JFLA2022/paper.tex
fix typos

\begin{abstract}
  \emph{Hydra-battles} is a collaborative library of commented proofs, developped under the \emph{Coq-Community} project.
  We present its evolution since a former presentation~\cite{JFLA2018paper} and how its structure is determined by other libraies and the \emph{Alectryon} literate proving tool.
\end{abstract}

@@

Hydra games (also known as \emph{Hydra battles}) appear in an article published in 1982 by two mathematicians, 
Laurie Kirby and Jeff Paris: \emph{Accessible Independence Results for Peano Arithmetic}~\cite{KP82}.
This article describes a game between two players: Hercules and a hydra.
A short description of the game  can be found in~\cite{bauer2008, KP82, JFLA2018paper}. One can also play with
Andrej Bauer's simulator~\cite{BauerHydra}.
In a few words:
\begin{itemize}
\item A hydra is a finite tree, traditionally presented with the root at the bottom, the leaves of which are called \emph{heads}
  (Fig~\ref{fig:round}).
\item At every round, Hercules chops off one head of the hydra. If the head is at a distance greater or equal than 2 from the root,
  then some sub-tree $h$ of the hydra is copied a certain amount $n$ of times. The number $n$ of copies and the sub-tree $h$ may depend of the considered variant of the game
  or the time elapsed since the beginning of the fight.
  Figure~\ref{fig:round} shows an example of such a transformation with $n=2$.
\end{itemize}

>>>>

\begin{abstract}
  \emph{Hydra-battles} is a collaborative library of commented proofs, developped under the \emph{Coq-Community} project.
  We present its evolution since a former presentation~\cite{JFLA2018paper} and how its structure is determined by other
  libraries and the \emph{Alectryon} literate proving tool.
\end{abstract}

@@

Hydra games (also known as \emph{Hydra battles}) appear in an article published in 1982 by two mathematicians, 
Laurie Kirby and Jeff Paris: \emph{Accessible Independence Results for Peano Arithmetic}~\cite{KP82}.
This article describes a game between two players: Hercules and a hydra.
A short description of the game  can be found in~\cite{bauer2008, KP82, JFLA2018paper}. One can also play with
Andrej Bauer's simulator~\cite{BauerHydra}.
In a few words:
\begin{itemize}
\item A hydra is a finite tree, traditionally presented with the root at the bottom, the leaves of which are called \emph{heads}
  (Fig~\ref{fig:round}).
\item At every round, Hercules chops off one head of the hydra. If the head is at a distance greater or equal than 2 from the root,
  then some sub-tree $h$ of the hydra is copied a certain amount $n$ of times. The number $n$ of copies and the sub-tree $h$ may depend of the considered variant of the game
  or the time elapsed since the beginning of the fight.
  Figure~\ref{fig:round} shows an example with $n=2$.
\end{itemize}
